---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Marcus Minko"
date: "02-02-2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox)
 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")

```

### Exercise 1

```{r dataset-dennys}

nrow(dennys)
ncol(dennys)

glimpse(dennys)

```
each row is a particular Denny's location, and the variables are address, city, state, zipcode, longitude, and latitude for each restaurant.

### Exercise 2

```{r dataset-laquinta}
nrow(dennys)
ncol(dennys)

glimpse(dennys)
```

same dataset except for laquinta locations

there are 17 non-US locations

you could figure out which locations were not in the us by the state variable, perhaps. Or maybe with the GPS coordinates.

### Exercise 3
```{r mutate-dennys-US}
dennys %>% 
     filter(!(state %in% states$abbreviation))
     
dennys %>% 
     mutate(country = "United States")     
```
...

### Exercise 4
``` {r mutate-lq-country}

lq <- laquinta %>%
               mutate(country = case_when(
                   state %in% state.abb     ~ "United States",
                   state %in% c("ON", "BC") ~ "Canada",
                   state == "ANT"           ~ "Colombia", 
                   state == "FM" ~ "Honduras", 
                   state %in% c("AG", "CH", "QR", "PU", "SL", "VE") ~ "Mexico"
               ))
glimpse(lq)
```
...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

