---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Marcus Minko"
date: "02-02-2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox)
 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")

```

### Exercise 1

```{r dataset-dennys}

nrow(dennys)
ncol(dennys)

glimpse(dennys)

```
each row is a particular Denny's location, and the variables are address, city, state, zipcode, longitude, and latitude for each restaurant.

### Exercise 2

```{r dataset-laquinta}
nrow(dennys)
ncol(dennys)

glimpse(dennys)
```

same dataset except for laquinta locations

there are 17 non-US locations

you could figure out which locations were not in the us by the state variable, perhaps. Or maybe with the GPS coordinates.

### Exercise 3
```{r mutate-dennys-US}
dennys %>% 
     filter(!(state %in% states$abbreviation))
     
dn <- dennys %>% 
     mutate(country = "United States")  

glimpse(dn)
```
...

### Exercise 4
``` {r mutate-lq-country}

lq <- laquinta %>%
               mutate(country = case_when(
                   state %in% state.abb     ~ "United States",
                   state %in% c("ON", "BC") ~ "Canada",
                   state == "ANT"           ~ "Colombia", 
                   state == "FM" ~ "Honduras", 
                   state %in% c("AG", "CH", "QR", "PU", "SL", "VE") ~ "Mexico"
               ))
glimpse(lq)
```
...

### Exercise 5
``` {r arrange-dennys-state}

dn %>% 
  count(state) %>%   
    arrange(desc(n))

dn %>% 
  count(state) %>% 
    arrange(n)
```
Most - CA, Least- DE Not surprising given the respective sizes and population densities of these states

```{r arrange-laquinta-state}

lq %>% 
     count(state) %>%   
     arrange(desc(n))

lq %>% 
    filter(country == "United States") %>% 
    count(state) %>%   
     arrange(n)
```
Most- TX, Least - ME Again, Not surprising given the respective sizes and population densities of these states

...


### Exercise 6
``` {r location-density-by-state}
dn %>%
          count(state) %>%
          inner_join(states, by = c("state" = "abbreviation")) %>% 
          mutate(location_density = area/n) %>% 
          arrange(location_density)

lq %>%
          count(state) %>%
          inner_join(states, by = c("state" = "abbreviation")) %>% 
          mutate(location_density = area/n) %>% 
          arrange(location_density)
```
Denny's- DC has the greatest density per square mile

La Quinta- RI has greatest density per square mile

### Exercise 7
``` {r viz-data}

dn <- dn %>%
  mutate(establishment = "Denny's")
lq <- lq %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(dn, lq)

ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point()

dn_lq %>% 
  filter(state == "NC") %>% 
ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment, alpha = .8)) + labs(title = "Denny's & La Quinta Locations", subtitle = "North Carolina") +
  geom_point() 

# It does appear to be true that most La Quinta locations are close to Denny's locations in North Carolina.

dn_lq %>% 
  filter(state == "TX") %>% 
ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment, alpha = .4)) + labs(title = "Denny's & La Quinta Locations", subtitle = "Texas") +
  geom_point()

# It also appears to be true that most La Quinta locations are close to Denny's locations in Texas.

```
...

 
Add exercise headings as needed.

